---
title: "March Time Trials"
description: |
  Two full months of time trial data!
author:
  - name: Sarah Johnson
categories:
  - time trials
date: 2022-04-13
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
library(lubridate)
```

My [first post](https://sarah.fyi/mk/2022-02-tt/) on this blog looked at my Mario Kart time trial data for February 2022, the first month I began tracking this data. I've been practicing time trials on-and-off for a few years, so I didn't expect any major time saves. In that post, most of the line graphs are flat because I was only improving my times by a handful of milliseconds. In contrast, when the [new tracks](https://sarah.fyi/mk/2022-03-29-wave-1/) were released I immediately saw major time saves as I learned the tracks.

But I've been interested in seeing how the graphs look over a longer period of time. I've been playing more regularly than ever before, and recently I've been changing up my build to improve my speed. I'm expecting to see larger time saves than in February.

This post reviews all my personal bests for MK8DX tracks in February and March, grouped by release group (nitro, retro, and bonus) and cup. I excluded the new tracks because this data is covered more extensively in the post linked above.

```{r}
abr <- read_csv("../_data/track-abbr.csv")

tt <- read_csv("../_data/time-trials.csv", 
               col_types = cols(total = "c")) %>% 
  filter(date < "2022-04-01") %>% 
  mutate(total = ms(total),
         yr = year(date),
         mth = month(date),
         day = day(date),
         hour = hour(time),
         min = minute(time),
         dt = make_datetime(year = yr, month = mth, day = day, hour = hour, min = min)) %>% left_join(abr)

tt3 <- tt %>% 
  filter(mth == 3)
```

```{r}
tt150 <- tt %>% 
  filter(cc == "150")

tt3150 <- tt3 %>% 
  filter(cc == "150")
```

### Nitro Tracks

```{r, layout="l-page", fig.height=5}
nitro <- tt150 %>% 
  filter(type == "nitro")

ggNitro <- ggplot(nitro, aes(x= dt, y=total, color = track)) +
  geom_point() +
  geom_line() +
  facet_grid(cols = vars(cup)) +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Track") +
  theme_minimal() +
  theme(legend.position = "none")

ggplotly(ggNitro)
```

### Retro Tracks

```{r, layout="l-page", fig.height=5}
retro <- tt150 %>% 
  filter(type == "retro")

ggRetro <- ggplot(retro, aes(x= dt, y=total, color = track)) +
  geom_point() +
  geom_line() +
  facet_grid(cols = vars(cup)) +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Track") +
  theme_minimal() +
  theme(legend.position = "none")

ggplotly(ggRetro)
```

### Bonus Tracks

```{r, layout="l-page", fig.height=5}
bonus <- tt150 %>% 
  filter(type == "DLC")

ggBonus <- ggplot(bonus, aes(x= dt, y=total, color = track)) +
  geom_point() +
  geom_line() +
  facet_grid(cols = vars(cup)) +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Track") +
  theme_minimal() +
  theme(legend.position = "none")

ggplotly(ggBonus)
```

Yep, the lines definitely get more fun to look at as more data is added. Downward trajectories are more noticeable. I can also see when I stall out on improving my times for tracks. I'll use these graphs as reference for which tracks I need to practice.

### Day of Month

Rather than my PBs being spread evenly across the month, 70% of my PBs occurred on five days: March 6th, 12th, 18th, 19th, and 25th.

```{r}
ggDay <- tt3 %>% 
  ggplot(aes(x = day)) +
  geom_bar() +
  theme_minimal() +
  labs(x = "Day",
       y = "PBs")

ggplotly(ggDay)
```

The new tracks were released on March 17th and I played nonstop the following week. The spike on March 12th is [when I switched](https://sarah.fyi/mk/2022-03-13-bittybuggy/) my kart from the City Tripper to the Biddybuggy.

### Time of Day

I wanted to see what time of day I set the most PBs and compare it to February. I began a new job in April and I tried to adjust my schedule to be less nocturnal during March.

Trying out a new graph so apologies if this format is awkward. The left side is February and March is on the right. The y-axis is the time of day, beginning and ending at midnight.

```{r}
ct <- tt %>% group_by(mth) %>% count(hour) %>% 
  rename(month = mth)

ggTime <- ct %>% 
  ggplot(aes(x = month, y=hour, fill=n)) +
  geom_tile() +
  theme_minimal() +
  scale_y_reverse() +
  labs(x = "",
       y = "",
       title = "PBs by time of day by month") +
  theme(legend.position = "none",
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        panel.background = element_blank(),
        panel.grid = element_blank())

ggplotly(ggTime)
```

Changes in my sleep schedule are reflected in the graph. In March I mostly PB'd before midnight and I played in the middle of the day, a time in February I would typically be asleep.

Is this a decent, roundabout way of tracking my sleep schedule? Idk. But it was fun to change up the data visualization from my normal bar/line graphs.
