---
title: "Mario Kart Time Trial PBs"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: sandstone
    navbar:
      - { icon: "fas fa-home", href: "https://sarah.fyi/index", align: right}
---

```{r}
library(tidyverse)
library(plotly)
library(lubridate)
```

```{r}
abr <- read_csv("_data/track-abbr.csv") 

tt <- read_csv("_data/time-trials.csv", 
               col_types = cols(total = "c")) %>% 
  filter(cc == 150) %>% 
  mutate(total = ms(total),
         yr = year(date),
         mth = month(date),
         day = day(date),
         hour = hour(time),
         min = minute(time),
         dt = make_datetime(year = yr, month = mth, day = day, hour = hour, min = min)) %>% 
  left_join(abr) %>%
  mutate(track = fct_reorder(track, trkNO))
```

# All Tracks

## Column 1

### Violin Plot

```{r fig.height=10}
tt %>% 
  filter(trk != "dBP") %>% 
  group_by(track) %>% 
  mutate(sd = sd(total)) %>% 
  ungroup() %>% 
  ggplot(aes(factor(track), total)) +
  geom_violin(draw_quantiles = 0.5, 
              scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) + 
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_y_time() +
  scale_x_discrete(limits = rev(levels(tt$track))) +
  coord_flip() +
  labs(x = "",
       y = "PB Time",
       title = "Time Trial PB Distributions (150cc)",
       subtitle = "February-April 2022") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")
```

## Column 2

### Average Time Save by Week

```{r}
ttDiff <- tt %>% 
  arrange(trk, dt) %>% 
  group_by(trk) %>% 
  mutate(prev = lag(total), .after = total,
         diff = as.double(prev - total, units = "secs"),
         diff = replace_na(diff, 0)
         ) %>% 
  mutate(cumsum = cumsum(diff), .after = diff)

wk <- ttDiff %>% 
  filter(!is.na(prev)) %>% 
  ungroup() %>% 
  mutate(week = week(date)) %>% 
  group_by(week) %>% 
  summarise(mean = mean(diff), n = n())

ggWk <- wk %>% 
  ggplot(aes(x=week, y=mean)) +
  geom_line() +
  theme_minimal()

ggplotly(ggWk)
```

### Number of PBs Each Week

```{r}
ggN <- wk %>% 
  ggplot(aes(x=week, y=n)) +
  geom_line() +
  theme_minimal()

ggplotly(ggN)
```



# Nitro Cups

## Column 1

### Mushroom Cup

sfs

### Flower Cup

dsfs

## Column 2

### Star Cup

sdfs

### Special cup

sdfsdf

# Retro Cups

## Column 1

### Shell Cup

sdfsd

### Banana Cup

dfsd

## Column 2

### Leaf Cup

sfsd

### Lightning Cup

sdfsdf

# Bonus Cups

## Column 1

### Egg Cup

sdfd

### Triforce Cup

sfsdf

## Crossing Cup

### Crossing Cup

sdfsd

### Bell Cup

sdfds

# DLC Cups

## Column 1

### Golden Dash Cup

sdfs

## Column 2

### Lucky Cat Cup

dfsdf