---
title: "Mario Kart Speedruns"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    favicon: favicon.png
    source_code: embed
    theme:
      version: 4
      bootswatch: minty
    navbar:
      - { icon: "fa fa-twitter", href: "https://twitter.com/sarah_fyi", alight: right }
      - { icon: "fa fa-twitch", href: "https://www.twitch.tv/sarahFYI", alight: right }
      - { icon: "fa fa-home", href: "https://sarah.fyi/", alight: right }
runtime: shiny
---

```{bash llstocsv, eval=FALSE, include=FALSE}
#' I use chipdelmal's MK8D package to 
#' convert all lss files in a folder to csv
#' https://github.com/Chipdelmal/MK8D
#' His blog was also the inspiration for the traces/violin plot. 
#' https://chipdelmal.github.io/
MK8D_trk2csv ./_data/splits ./_data/splits MK8D_trks.csv
```

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(plotly)
library(emojifont)

#' This is my first shiny-ish app. 
#' very unoptimized b/c idk what I'm doing (how do reactives work??). 
#' The data is currently hosted on my website's GH,  
#' https://github.com/sj-io/sarahFYI, 
```

```{r getData, include=FALSE}
source("lsstocsv.R")
```

## Welcome {.sidebar}


<small>An overview of my **Mario Kart 8 Deluxe** (**MK8D**) 150cc speedruns.</small>

```{r}
selectInput("v_cat2", label = "Select a Category:", choices = ct2)
```

<small>

```{r}
checkboxInput("v_star", label = "Best splits")
checkboxInput("v_poop", label = "Worst splits")
```


<details><summary>Show/Hide explanation of data, graphs, and speedrunning.</summary>
<p></p>

**Speedrunning** is trying to complete a game as fast as possible. Each speedrunning attempt is called a **run**. Each segment of a run is called a **split** (synonymous with "track" in Mario Kart). The most popular way to speedrun MK8D is to play through all of the original 48 tracks, which takes about two hours on 150cc. Other categories include 16 track runs and 4 track cup runs. Use the dropdown above to change the category.

The **Run Duration over Time** graph shows how my run times have changed (usually decreasing & improving) since I began running. 

The **Improvement from Slowest Run** graph shows this data with more detail. Each line is a completed run, comparing my cumulative run time for each track to that of my slowest run. The lowest colored line is my current **personal best** (**PB**), AKA the fastest time I've run the category. 

The orange dots show tracks where my PB run had a slower time than a previous run, indicating a **possible time save**; the size of the dot indicates how much time save is available. The grey line is my hypothetical **best possible time**, the cumulative sum of my best time for each track across all run attempts. Hover over any point/line for more detail.

The poop emojis shows my worst splits; the star emojis show my best splits.

Overlayed on the graph is a violin plot for each track. The color of each violin is relative to the track's **standard deviation**. The more spread out a track time's are relative to the other tracks, the lighter the color of its violin.
</details>
<p></p>
Created by [Sarah Johnson](https://sarah.fyi/).
</small>

## Top Storyboard {.storyboard}

```{r include=FALSE}
#' rn_a = All Runs, rn_c = Completed Runs
#' tbh I don't understand how these work or why they fail half the time I try to use them
rn_a <- reactive({runs %>% filter(cat2 == input$v_cat2)})
rn_c <- reactive({sr %>% filter(cat2 == input$v_cat2)})
```

### Most Recent Attempt

```{r}
renderValueBox({
  recentRun0 <- rn_a()
  
  recentRun <- max(recentRun0$date)
  
  valueBox(
    value = recentRun,
    icon = "fa fa-calendar"
  )
})
```

### Current Personal Best

```{r}
renderValueBox({
  PB <- runs %>%
    filter(cat2 == input$v_cat2 & !is.na(pts))
  
  P <- round(seconds_to_period(max(PB$cumsum)), 3)
  
  D <- unique(PB$date)
  
  PD <-
    paste0(P, "<br>", "<p style=\"font-size:10px\">", "Set on ", D, "</p>")
  
  valueBox(value = HTML(PD),
           icon = "fa fa-splotch")
})
```


### Best Possible Time

```{r}
renderValueBox({
  valBPT0 <- runs %>% 
    filter(cat2 == input$v_cat2 & ID == "Best Possible Time")
  
  valBPT <- round(seconds_to_period(max(valBPT0$cumsum)), 3)
  
  valueBox(
    value = valBPT,
    icon = "fa fa-trophy"
  )
})
```

### Possible Time Save

```{r}
renderValueBox({
  valPTS <- runs %>% 
    filter(cat2 == input$v_cat2 & !is.na(pts)) %>% 
    summarise(round(seconds_to_period(sum(pts)), 3))
  
  valueBox(
    value = valPTS,
    icon = "fa fa-clock"
  )
})
```

##  Middle Row Here! 

### Run Duration over Time {data-width=300}

```{r warning=FALSE}
renderPlotly({
  ggLine <- run_time %>%
    filter(cat2 == input$v_cat2) %>%
    mutate(label = paste0(
      "<b>Run #",
      runNO,
      " ",
      date,
      "</b>",
      "<br>",
      round(seconds_to_period(cumsum), 2)
    )) %>%
    ggplot(aes(runNO, cumsum, color = "goldenrod")) +
    geom_line() +
    geom_point(aes(text = label)) +
    scale_y_time(labels = scales::label_time()) +
    scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
    scale_color_identity() +
    labs(x = "Run Number", y = "") +
    theme_minimal() +
    theme(axis.ticks = element_line(size = .2),
          panel.border = element_rect(fill = NA, size = .2),
          legend.position = "none")
  
  ggplotly(ggLine, tooltip = "text")
})
```

### Improvement from Slowest Run

```{r warning=FALSE}
renderPlotly({
  rn <- runs %>%
    group_by(cat2, track) %>%
    mutate(sd = sd(time)) %>%
    ungroup() %>%
    filter(cat2 == input$v_cat2)
  
  # name colors
  colors <- color_range(length(unique(rn$runNO)))
  rn <- rn %>%
    mutate(clr = ifelse(runNO == 0, "grey",
                        colors[rn$runNO]))
  
  # traces plot
  ggTraces <- ggplot() +
    geom_violin(
      data = rn[which(rn$runNO != 0),],
      aes(
        factor(track),
        maxdiff,
        color = NA,
        fill = sd,
        alpha = .1
      ),
      scale = "width"
    ) +
    geom_line(data = rn,
              aes(
                factor(track),
                maxdiff,
                group = runNO,
                color = clr,
                alpha = runNO,
                text = label
              )) +
    geom_point(data = rn[which(rn$pts > 0),],
               aes(
                 factor(track),
                 maxdiff,
                 size = pts,
                 color = "tomato",
                 text = label
               )) +
    scale_y_time() +
    scale_fill_gradient(low = "darkcyan", high = "plum") +
    scale_size_continuous(range = c(.5, 2.75)) +
    scale_color_identity() +
    scale_alpha_continuous(range = c(.35, .8)) +
    labs(x = "",
         y = "") +
    theme_minimal() +
    theme(
      axis.text.x = element_text(
        angle = 45,
        hjust = 0.98,
        vjust = 0.9
      ),
      axis.text = element_text(size = 8),
      axis.ticks = element_line(size = .2),
      panel.grid = element_line(size = .2),
      panel.border = element_rect(fill = NA, size = .2),
      legend.position = "none"
    )
  
  # The style component omits the violin plot's tooltip
  gtp <- ggplotly(ggTraces, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  
  #' add best/work track emojis 
  #' lmao this is definitely not how this is supposed to be done
  #' but it works for now
  if (input$v_poop == TRUE & input$v_star == FALSE) {
    poop <- ggTraces +
      geom_text(
      data = rn[which(rn$worst == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("poop"),
      family = 'EmojiOne',
      size = 3)
    
    ggplotly(poop, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  } else if (input$v_poop == TRUE & input$v_star == TRUE) {
    poopstar <- ggTraces +
      geom_text(
      data = rn[which(rn$worst == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("poop"),
      family = 'EmojiOne',
      size = 3) +
      geom_text(
      data = rn[which(rn$best == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("star"),
      family = 'EmojiOne',
      size = 3)
    
    ggplotly(poopstar, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  } else if (input$v_poop == FALSE & input$v_star == TRUE) {
    star <- ggTraces +
      geom_text(
      data = rn[which(rn$best == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("star"),
      family = 'EmojiOne',
      size = 3)
    
    ggplotly(star, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  } else {
    gtp
  }
  
})
```

### Improvement from Slowest Run {.mobile}

```{r warning=FALSE}
renderPlotly({
  rn <- runs %>% 
    group_by(cat2, track) %>% 
    mutate(sd = sd(time)) %>% 
    ungroup() %>% 
    filter(cat2 == input$v_cat2)
  
  # name colors
  colors <- color_range(length(unique(rn$runNO)))
  rn <- rn %>%
    mutate(
      clr = ifelse(runNO == 0, "grey", 
                   colors[rn$runNO]))
  
  
  # traces plot
  ggTraces <- ggplot() +
    geom_violin(data = rn[which(rn$runNO != 0), ],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
    geom_line(data = rn,
              aes(
                factor(track),
                maxdiff,
                group = runNO,
                color = clr,
                alpha = runNO,
                text = label
              )) +
    geom_point(data = rn[which(rn$pts > 0), ],
               aes(
                 factor(track),
                 maxdiff,
                 size = pts,
                 color = "tomato",
                 text = label
               )) +
    scale_y_time() +
    scale_x_discrete(limits = rev) +
    coord_flip() +
    scale_fill_gradient(low = "darkcyan", high = "plum") +
    scale_size_continuous(range = c(.5, 2.75)) +
    scale_color_identity() +
    scale_alpha_continuous(range = c(.35, .8)) +
    labs(x = "",
         y = "") +
    theme_minimal() +
    theme(
      axis.text.x = element_text(
        angle = 45,
        hjust = 0.98,
        vjust = 0.9
      ),
      axis.text = element_text(size = 8),
      axis.ticks = element_line(size = .2),
      panel.grid = element_line(size = .2),
      panel.border = element_rect(fill = NA, size = .2),
      legend.position = "none"
    )
  
  # The style component omits the violin plot's tooltip
  gtp <- ggplotly(ggTraces, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  
  #' add best/work track emojis 
  #' lmao this is definitely not how this is supposed to be done
  #' but it works for now
  if (input$v_poop == TRUE & input$v_star == FALSE) {
    poop <- ggTraces +
      geom_text(
      data = rn[which(rn$worst == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("poop"),
      family = 'EmojiOne',
      size = 3)
    
    ggplotly(poop, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  } else if (input$v_poop == TRUE & input$v_star == TRUE) {
    poopstar <- ggTraces +
      geom_text(
      data = rn[which(rn$worst == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("poop"),
      family = 'EmojiOne',
      size = 3) +
      geom_text(
      data = rn[which(rn$best == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("star"),
      family = 'EmojiOne',
      size = 3)
    
    ggplotly(poopstar, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  } else if (input$v_poop == FALSE & input$v_star == TRUE) {
    star <- ggTraces +
      geom_text(
      data = rn[which(rn$best == "yes"),],
      aes(factor(track), maxdiff, text = label),
      label = emoji("star"),
      family = 'EmojiOne',
      size = 3)
    
    ggplotly(star, tooltip = c("text")) %>%
    style(hoverinfo = "skip", traces = 0:length(unique(rn$track)))
  } else {
    gtp
  }
  
})
```

## Bottom Storyboard {.storyboard}

### Completed / Attempted Runs

```{r}
renderValueBox({
  completes <- rn_a() %>%
    filter(ID != "Best Possible Time") %>%
    distinct(ID) %>% 
    count()
  
  attempts <- rn_c() %>% 
    distinct(ID) %>%
    count()
  
  runAttempts <- paste(completes, "/", attempts)
  
  valueBox(
    value = runAttempts,
    icon = "fa fa-flag-checkered"
  )
})
```

### Oldest Gold

```{r}
renderValueBox({
  valBPT0 <- runs %>% 
    filter(cat2 == input$v_cat2 & ID == "Best Possible Time" & track != " ")
  
  BP <- valBPT0 %>% 
    slice_min(PBdate, with_ties = FALSE)
  
  BP2 <-
    paste0(BP$track, "<br>", "<p style=\"font-size:10px\">Set on ", BP$PBdate, "</p>")
  
  valueBox(value = HTML(BP2),
           icon = "fa fa-skull")
})
```

### Number of Tracks with Time Save Available

```{r}
renderValueBox({
  PBB <- runs %>%
    filter(cat2 == input$v_cat2 & pts > 0) %>% 
    count()
  
  valueBox(value = PBB,
           icon = "fa fa-stopwatch")
})
```

### Largest Time Save Available

```{r}
renderValueBox({
  WT <- runs %>% 
    filter(cat2 == input$v_cat2 & !is.na(pts)) %>% 
    slice_max(pts, with_ties = FALSE)
  
  PC <-
    paste0(round(seconds_to_period(max(WT$pts)), 3), "<br>", 
           "<p style=\"font-size:10px\">", WT$track, "</p>")
  
  valueBox(value = HTML(PC),
           icon = "fa fa-poo")
})
```
