---
title: "Mario Kart Speedruns"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    navbar:
      - { title: "Time Trials", href: "tt.hrml", align: right}
      - { icon: "fas fa-home", href: "index.html", align: right}
    theme:
      bootswatch: minty
    favicon: blueshell.png
    source_code: embed
---

```{bash llstocsv, include=FALSE}
# Convert all lss files in folder to csv
MK8D_trk2csv ./_data/splits ./_data/splits MK8D_trks.csv
```

```{r libs}
library(tidyverse)
library(lubridate)
library(plotly)
```

```{r}
source("lsstocsv.R")

sr <- sr %>% 
  group_by(cat2, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()
```

# 48 Tracks

## Col 1 {data-width="350"}

### Track Time Distributions

```{r}
violin_48 <- sr %>% 
  filter(cat2 == "Original 48" & track != "Start") %>% 
  ggplot(aes(factor(track), time)) +
  geom_violin(scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) +
  stat_summary(fun = "mean", geom = "crossbar", size = .2, aes(color = sd)) +
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_color_gradient(low = "darkcyan", high = "plum") +
  scale_y_time() +
  scale_x_discrete(limits = rev) +
  coord_flip() +
  labs(x = "",
       y = "Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(violin_48)
```

## Col 2 {.tabset}

### Improvement

```{r}
runs_48 <- runs %>% 
  filter(cat2 == "Original 48") %>% 
  group_by(cat2, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()

colors_48 <- color_range(length(unique(runs_48$runNO)))

runs_48 <- runs_48 %>% 
  mutate(clr = ifelse(runNO == 0, "grey", colors_48[runs_48$runNO]))
```

```{r}
traces_48 <- ggplot() +
  geom_violin(data = runs_48[which(runs_48$runNO != 0), ],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
  geom_line(data = runs_48, aes(
    factor(track),
    maxdiff,
    group = runNO,
    color = clr,
    alpha = runNO,
    text = label
  )) +
  geom_point(data = runs_48[which(runs_48$pts > 0),], aes(
    factor(track), 
    maxdiff, 
    size = pts,
    color = "tomato",
    text = label)) +
  scale_y_time() +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_size_continuous(range = c(.05, 2.75)) +
  scale_color_identity() +
  scale_alpha_continuous(range = c(.35, .8)) +
  labs(x = "",
       y = "") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0.98,
      vjust = 0.9
    ),
    axis.text = element_text(size = 8),
    axis.ticks = element_line(size = .2),
    panel.grid = element_line(size = .2),
    panel.border = element_rect(fill = NA, size = .2),
    legend.position = "none"
  )



ggplotly(traces_48, tooltip = "text") %>% 
  layout(margin = list(t = 60),
    title = list(text = paste0('Improvement from Slowest Run',
                                    '<br><sup>48 Tracks, 150cc, No Items</sup>'))) %>% 
  style(hoverinfo = "skip", traces = 0:length(unique(runs_48$track)))
```

### Run Time

```{r}
run_time_48 <- run_time %>%
  filter(cat2 == "Original 48") %>%
  mutate(label = paste0(
    "<b>Run #",
    runNO,
    " ",
    date,
    "</b>",
    "<br>",
    round(seconds_to_period(cumsum), 2)
  )) %>%
  ggplot(aes(runNO, cumsum, color = "goldenrod")) +
  geom_line() +
  geom_point(aes(text = label)) +
  scale_y_time(labels = scales::label_time()) +
  scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
  scale_color_identity() +
  labs(x = "Run Number", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(run_time_48, tooltip = "text")
```

# Nitro Tracks {data-navmenu="16 Tracks"}

## Col 1 {data-width="350"}

### Track Time Distributions

```{r}
violin_nt <- sr %>% 
  filter(cat2 == "Nitro Tracks" & track != "Start") %>% 
  ggplot(aes(factor(track), time)) +
  geom_violin(scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) +
  stat_summary(fun = "mean", geom = "crossbar", size = .2, aes(color = sd)) +
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_color_gradient(low = "darkcyan", high = "plum") +
  scale_y_time() +
  scale_x_discrete(limits = rev) +
  coord_flip() +
  labs(x = "",
       y = "Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(violin_nt)
```

## Col 2 {.tabset}

### Improvement

```{r}
runs_nt <- runs %>% 
  filter(cat2 == "Nitro Tracks") %>% 
  group_by(cat2, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()

colors_nt <- color_range(length(unique(runs_nt$runNO)))

runs_nt <- runs_nt %>% 
  mutate(clr = ifelse(runNO == 0, "grey", colors_nt[runs_nt$runNO]))
```

```{r}
traces_nt <- ggplot() +
  geom_violin(data = runs_nt[which(runs_nt$runNO != 0),],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
  geom_line(data = runs_nt, aes(
    factor(track),
    maxdiff,
    group = runNO,
    color = clr,
    alpha = runNO,
    text = label
  )) +
  geom_point(data = runs_nt[which(runs_nt$pts > 0),], aes(
    factor(track), 
    maxdiff, 
    size = pts,
    color = "tomato",
    text = label)) +
  scale_y_time() +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_size_continuous(range = c(.05, 2.75)) +
  scale_color_identity() +
  scale_alpha_continuous(range = c(.35, .8)) +
  labs(x = "",
       y = "") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0.98,
      vjust = 0.9
    ),
    axis.text = element_text(size = 8),
    axis.ticks = element_line(size = .2),
    panel.grid = element_line(size = .2),
    panel.border = element_rect(fill = NA, size = .2),
    legend.position = "none"
  )



ggplotly(traces_nt, tooltip = "text") %>% 
  layout(margin = list(t = 60),
    title = list(text = paste0('Improvement from Slowest Run',
                                    '<br><sup>Nitro Tracks, 150cc, No Items</sup>'))) %>% 
  style(hoverinfo = "skip", traces = 0:length(unique(runs_nt$track)))
```

### Run Time

```{r}
run_time_nt <- run_time %>%
  filter(cat2 == "Nitro Tracks") %>%
  mutate(label = paste0(
    "<b>Run #",
    runNO,
    " ",
    date,
    "</b>",
    "<br>",
    round(seconds_to_period(cumsum), 2)
  )) %>%
  ggplot(aes(runNO, cumsum, color = "goldenrod")) +
  geom_line() +
  geom_point(aes(text = label)) +
  scale_y_time(labels = scales::label_time()) +
  scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
  scale_color_identity() +
  labs(x = "Run Number", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(run_time_nt, tooltip = "text")
```

# Nitro Cups {data-navmenu="Cups"}

## Col 1 {data-width="350"}

### Track Time Distributions

```{r}
violin_nc <- sr %>% 
  filter(cat1 == "Nitro Cups" & track != "Start") %>% 
  ggplot(aes(factor(track), time)) +
  geom_violin(scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) +
  stat_summary(fun = "mean", geom = "crossbar", size = .2, aes(color = sd)) +
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_color_gradient(low = "darkcyan", high = "plum") +
  scale_y_time() +
  scale_x_discrete(limits = rev) +
  coord_flip() +
  labs(x = "",
       y = "Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(violin_nc)
```

## Col 2 {.tabset}

### Improvement

```{r}
runs_nc <- runs %>% 
  filter(cat1 == "Nitro Cups") %>% 
  group_by(cat1, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()

colors_nc <- color_range(length(unique(runs_nc$runNO)))

runs_nc <- runs_nc %>% 
  mutate(clr = ifelse(runNO == 0, "grey", colors_nc[runs_nc$runNO]))
```

```{r}
traces_nc <- ggplot() +
  geom_violin(data = runs_nc[which(runs_nc$runNO != 0), ],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
  geom_line(data = runs_nc, aes(
    factor(track),
    maxdiff,
    group = runNO,
    color = clr,
    alpha = runNO,
    text = label
  )) +
  geom_point(data = runs_nc[which(runs_nc$pts > 0),], aes(
    factor(track), 
    maxdiff, 
    size = pts,
    color = "tomato",
    text = label)) +
  scale_y_time() +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_size_continuous(range = c(.05, 2.75)) +
  scale_color_identity() +
  scale_alpha_continuous(range = c(.35, .8)) +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "",
       y = "") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0.98,
      vjust = 0.9
    ),
    axis.text = element_text(size = 8),
    axis.ticks = element_line(size = .2),
    panel.grid = element_line(size = .2),
    panel.border = element_rect(fill = NA, size = .2),
    legend.position = "none"
  )



ggplotly(traces_nc, tooltip = "text") %>% 
  layout(margin = list(b = 110)) %>% 
  style(hoverinfo = "skip", traces = 0:length(unique(runs_nc$track)))
```

### Run Time

```{r}
run_time_nc <- run_time %>%
  filter(cat1 == "Nitro Cups") %>%
  mutate(label = paste0(
    "<b>Run #",
    runNO,
    " ",
    date,
    "</b>",
    "<br>",
    round(seconds_to_period(cumsum), 2)
  )) %>%
  ggplot(aes(runNO, cumsum, color = "goldenrod")) +
  geom_line() +
  geom_point(aes(text = label)) +
  scale_y_time(labels = scales::label_time()) +
  scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
  scale_color_identity() +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "Run Number", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(run_time_nc, tooltip = "text")
```

# Retro Cups {data-navmenu="Cups"}

## Col 1 {data-width="350"}

### Track Time Distributions

```{r}
violin_rc <- sr %>% 
  filter(cat1 == "Retro Cups" & track != "Start") %>% 
  ggplot(aes(factor(track), time)) +
  geom_violin(scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) +
  stat_summary(fun = "mean", geom = "crossbar", size = .2, aes(color = sd)) +
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_color_gradient(low = "darkcyan", high = "plum") +
  scale_y_time() +
  scale_x_discrete(limits = rev) +
  coord_flip() +
  labs(x = "",
       y = "Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(violin_rc)
```

## Col 2 {.tabset}

### Improvement

```{r}
runs_rc <- runs %>% 
  filter(cat1 == "Retro Cups") %>% 
  group_by(cat1, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()

colors_rc <- color_range(length(unique(runs_rc$runNO)))

runs_rc <- runs_rc %>% 
  mutate(clr = ifelse(runNO == 0, "grey", colors_rc[runs_rc$runNO]))
```

```{r}
traces_rc <- ggplot() +
  geom_violin(data = runs_rc[which(runs_rc$runNO != 0), ],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
  geom_line(data = runs_rc, aes(
    factor(track),
    maxdiff,
    group = runNO,
    color = clr,
    alpha = runNO,
    text = label
  )) +
  geom_point(data = runs_rc[which(runs_rc$pts > 0),], aes(
    factor(track), 
    maxdiff, 
    size = pts,
    color = "tomato",
    text = label)) +
  scale_y_time() +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_size_continuous(range = c(.05, 2.75)) +
  scale_color_identity() +
  scale_alpha_continuous(range = c(.35, .8)) +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "",
       y = "") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0.98,
      vjust = 0.9
    ),
    axis.text = element_text(size = 8),
    axis.ticks = element_line(size = .2),
    panel.grid = element_line(size = .2),
    panel.border = element_rect(fill = NA, size = .2),
    legend.position = "none"
  )



ggplotly(traces_rc, tooltip = "text") %>% 
  layout(margin = list(b = 110)) %>% 
  style(hoverinfo = "skip", traces = 0:length(unique(runs_rc$track)))
```

### Run Time

```{r}
run_time_rc <- run_time %>%
  filter(cat1 == "Retro Cups") %>%
  mutate(label = paste0(
    "<b>Run #",
    runNO,
    " ",
    date,
    "</b>",
    "<br>",
    round(seconds_to_period(cumsum), 2)
  )) %>%
  ggplot(aes(runNO, cumsum, color = "goldenrod")) +
  geom_line() +
  geom_point(aes(text = label)) +
  scale_y_time(labels = scales::label_time()) +
  scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
  scale_color_identity() +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "Run Number", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(run_time_rc, tooltip = "text")
```

# Bonus Cups {data-navmenu="Cups"}

## Col 1 {data-width="350"}

### Track Time Distributions

```{r}
violin_bc <- sr %>% 
  filter(cat1 == "Bonus Cups" & track != "Start") %>% 
  ggplot(aes(factor(track), time)) +
  geom_violin(scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) +
  stat_summary(fun = "mean", geom = "crossbar", size = .2, aes(color = sd)) +
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_color_gradient(low = "darkcyan", high = "plum") +
  scale_y_time() +
  scale_x_discrete(limits = rev) +
  coord_flip() +
  labs(x = "",
       y = "Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(violin_bc)
```

## Col 2 {.tabset}

### Improvement

```{r}
runs_bc <- runs %>% 
  filter(cat1 == "Bonus Cups") %>% 
  group_by(cat1, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()

colors_bc <- color_range(length(unique(runs_bc$runNO)))

runs_bc <- runs_bc %>% 
  mutate(clr = ifelse(runNO == 0, "grey", colors_bc[runs_bc$runNO]))
```

```{r}
traces_bc <- ggplot() +
  geom_violin(data = runs_bc[which(runs_bc$runNO != 0), ],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
  geom_line(data = runs_bc, aes(
    factor(track),
    maxdiff,
    group = runNO,
    color = clr,
    alpha = runNO,
    text = label
  )) +
  geom_point(data = runs_bc[which(runs_bc$pts > 0),], aes(
    factor(track), 
    maxdiff, 
    size = pts,
    color = "tomato",
    text = label)) +
  scale_y_time() +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_size_continuous(range = c(.05, 2.75)) +
  scale_color_identity() +
  scale_alpha_continuous(range = c(.35, .8)) +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "",
       y = "") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0.98,
      vjust = 0.9
    ),
    axis.text = element_text(size = 8),
    axis.ticks = element_line(size = .2),
    panel.grid = element_line(size = .2),
    panel.border = element_rect(fill = NA, size = .2),
    legend.position = "none"
  )



ggplotly(traces_bc, tooltip = "text") %>% 
  layout(margin = list(b = 110)) %>% 
  style(hoverinfo = "skip", traces = 0:length(unique(runs_bc$track)))
```

### Run Time

```{r}
run_time_bc <- run_time %>%
  filter(cat1 == "Bonus Cups") %>%
  mutate(label = paste0(
    "<b>Run #",
    runNO,
    " ",
    date,
    "</b>",
    "<br>",
    round(seconds_to_period(cumsum), 2)
  )) %>%
  ggplot(aes(runNO, cumsum, color = "goldenrod")) +
  geom_line() +
  geom_point(aes(text = label)) +
  scale_y_time(labels = scales::label_time()) +
  scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
  scale_color_identity() +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "Run Number", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(run_time_bc, tooltip = "text")
```

# DLC Cups {data-navmenu="Cups"}

## Col 1 {data-width="350"}

### Track Time Distributions

```{r}
violin_dc <- sr %>% 
  filter(cat1 == "DLC Cups" & track != "Start") %>% 
  ggplot(aes(factor(track), time)) +
  geom_violin(scale = "width",
              aes(fill = sd, color=sd),
              alpha = .7) +
  stat_summary(fun = "mean", geom = "crossbar", size = .2, aes(color = sd)) +
  stat_summary(fun = "median", geom = "point", size = .4) +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_color_gradient(low = "darkcyan", high = "plum") +
  scale_y_time() +
  scale_x_discrete(limits = rev) +
  coord_flip() +
  labs(x = "",
       y = "Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 0.98,
                                   vjust = 0.9),
        axis.text = element_text(size = 8),
        axis.ticks = element_line(size = .2),
        panel.grid = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(violin_dc)
```

## Col 2 {.tabset}

### Improvement

```{r}
runs_dc <- runs %>% 
  filter(cat1 == "DLC Cups") %>% 
  group_by(cat1, track) %>% 
  mutate(sd = sd(time)) %>% 
  ungroup()

colors_dc <- color_range(length(unique(runs_dc$runNO)))

runs_dc <- runs_dc %>% 
  mutate(clr = ifelse(runNO == 0, "grey", colors_dc[runs_dc$runNO]))
```

```{r}
traces_dc <- ggplot() +
  geom_violin(data = runs_dc[which(runs_dc$runNO != 0), ],
                aes(
                  factor(track), 
                  maxdiff,
                  color = NA,
                  fill = sd,
                  alpha = .1),
                scale = "width") +
  geom_line(data = runs_dc, aes(
    factor(track),
    maxdiff,
    group = runNO,
    color = clr,
    alpha = runNO,
    text = label
  )) +
  geom_point(data = runs_dc[which(runs_dc$pts > 0),], aes(
    factor(track), 
    maxdiff, 
    size = pts,
    color = "tomato",
    text = label)) +
  scale_y_time() +
  scale_fill_gradient(low = "darkcyan", high = "plum") +
  scale_size_continuous(range = c(.05, 2.75)) +
  scale_color_identity() +
  scale_alpha_continuous(range = c(.35, .8)) +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "",
       y = "") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 0.98,
      vjust = 0.9
    ),
    axis.text = element_text(size = 8),
    axis.ticks = element_line(size = .2),
    panel.grid = element_line(size = .2),
    panel.border = element_rect(fill = NA, size = .2),
    legend.position = "none"
  )



ggplotly(traces_dc, tooltip = "text") %>% 
  layout(margin = list(b = 110)) %>% 
  style(hoverinfo = "skip", traces = 0:length(unique(runs_dc$track)))
```

### Run Time

```{r}
run_time_dc <- run_time %>%
  filter(cat1 == "DLC Cups") %>%
  mutate(label = paste0(
    "<b>Run #",
    runNO,
    " ",
    date,
    "</b>",
    "<br>",
    round(seconds_to_period(cumsum), 2)
  )) %>%
  ggplot(aes(runNO, cumsum, color = "goldenrod")) +
  geom_line() +
  geom_point(aes(text = label)) +
  scale_y_time(labels = scales::label_time()) +
  scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
  scale_color_identity() +
  facet_wrap(~cat2, scales = "free") +
  labs(x = "Run Number", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_line(size = .2),
        panel.border = element_rect(fill = NA, size = .2),
        legend.position = "none")

ggplotly(run_time_dc, tooltip = "text")
```
