---
title: "February Time Trials"
description: |
  Reviewing my time trials PBs for February 2022.
author:
  - name: Sarah Johnson
categories:
  - time trials
date: 2022-03-09
output:
  distill::distill_article:
    self_contained: false
    toc: true
draft: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
library(lubridate)
```

In February 2022, I began keeping a spreadsheet of every time new personal best I set in Mario Kart time trials.

```{r}
tt <- read_csv("../_data/time-trials.csv", 
               col_types = cols(total = "c")) %>% 
  filter(date < "2022-03-01") %>% 
  mutate(total = ms(total),
         yr = year(date),
         mth = month(date),
         day = day(date),
         hour = hour(time),
         min = minute(time),
         dt = make_datetime(year = yr, month = mth, day = day, hour = hour, min = min)) 
```

## Nitro Tracks

The nitro tracks include the Mushroom, Flower, Star, and Special Cups. I set 28 PBs in nitro tracks in February.

```{r}
nitro <- tt %>% 
  filter(str_detect(cup, "Mushroom|Flower|Star|Special"))

nitro %>% count(track) %>% arrange(desc(n))
```

Mario Circuit, Thwomp Ruins, and Twisted Mansion tied for the most PBs set of the Nitro tracks. No PB was set for Shy Guy Falls.

```{r}
ggNitro <- ggplot(nitro, aes(x= dt, y=total, color = track)) +
  geom_point() +
  geom_line() +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Track") +
  theme_minimal()
```

```{r, layout="l-page", fig.height=6}
ggplotly(ggNitro)
```

## Retro Tracks

The retro tracks include Shell, Banana, Leaf, and Lightning Cups. I set 59 PBs in retro tracks in February.

```{r}
retro <- tt %>% 
  filter(str_detect(cup, "Shell|Banana|Leaf|Lightning"))

retro %>% count(track) %>% arrange(desc(n))
```

Donut Plains saw the most PBs of any track, by far. This was the first month I began taking the underwater shortcuts, so I practiced them extensively.

```{r}
ggRetro <- ggplot(retro, aes(x= dt, y=total, color = track)) +
  geom_point() +
  geom_line() +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Track") +
  theme_minimal()
```

```{r, layout="l-page", fig.height=6}
ggplotly(ggRetro)
```

## Bonus Tracks

The bonus tracks include the Egg, Crossing, Triforce, and Bell Cups. I set 39 PBs in Bonus Tracks during February.

```{r}
bonus <- tt %>% 
  filter(str_detect(cup, "Egg|Crossing|Triforce|Bell"))

bonus %>% count(track) %>% arrange(desc(n))
```

SNES Rainbow Road saw the most PBs, followed by Big Blue.

```{r}
ggBonus <- ggplot(bonus, aes(x= dt, y=total, color = track)) +
  geom_point() +
  geom_line() +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Track") +
  theme_minimal()
```

```{r, layout="l-page", fig.height=6}
ggplotly(ggBonus)
```

## All Tracks

In total, I set 126 PBs in February across 47 tracks (all except Shy Guy Falls).

```{r}
gg <- ggplot(tt, aes(x= dt, y=total, color = cup, group = track)) +
  geom_point() +
  geom_line() +
  scale_y_time() +
  labs(x = "",
       y = "",
       color = "Cup") +
  theme_minimal()
```

```{r, layout = "l-page", fig.height=6}
ggplotly(gg)
```

Towards the end of the month I focused on getting a PB in every track, using soft drifting, and nailing mushroomless skips.

### Day of Month

```{r}
ggDay <- tt %>% 
  ggplot(aes(x = day)) +
  geom_bar() +
  theme_minimal()

ggplotly(ggDay)
```

I set the most PBs on February 3rd (18), followed by the 14th (happy Valentine's Day to me lol) and 26th (16 each).

### Day of Week

```{r}
ggWday <- tt %>%
  mutate(wday = wday(date, label = TRUE)) %>% 
  ggplot(aes(x = wday)) +
  geom_bar() +
  theme_minimal()

ggplotly(ggWday)
```

I set the most PBs on Wednesdays, followed by Saturdays. Tuesday and Fridays saw the fewest PBs.

### Time of Day

```{r}
ggTime <- tt %>% 
  ggplot(aes(x = hour)) +
  geom_bar() +
  theme_minimal()

ggplotly(ggTime)
```

I set the vast majority of my PBs at night, particularly between 1-2 AM. No PBs were set between 11AM and 4PM.
