---
title: "Clint Stevens Mario Kart extended universe"
description: |
  Clint plays the new tracks with chat.
author:
  - name: Sarah Johnson
categories:
  - online
date: 2022-04-04
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
library(plotly)
library(DT)
```

```{r}
tracks <- read_csv("../_data/track-abbr.csv")

snipe <- read_csv("../_data/stream-snipe.csv",
                    col_types = list(.default = col_character()))
```

## Intro

Per [my](https://sarah.fyi/mk/2022-03-08-snipe/) [previous](https://sarah.fyi/mk/2022-03-11-snipe-guide/) [posts](https://sarah.fyi/mk/2022-03-15-snipe/), I've been tracking data on who plays in Clint Steven's online Mario Kart games and how they place. This post mostly shows data from games played on March 18th/19th, the day new tracks were released. Clint typically plays online in worldwide mode, usually joining a full lobby and requiring snipers to wait for a spot to open. Once in, there is no limit to how many games a person can play. This day, Clint created a room to play with people on his friends list, and he reset the room after eight games, allowing more people the chance to join.

Unfortunately I wasn't able to join a room on release day. However, another streamer, [swushwoi](https://www.twitch.tv/swushwoi), played later that day and many of the players in her lobby overlapped with Clint's. They were kind enough to let me play so I got my MK fix and I collected results from her games as well.[^1]

[^1]: Thus begins the Clint Stevens Mario Kart extended universe

At the bottom of the post you can find Clint's best and worst tracks and the overall player rankings for 2022. Feel free to use the table of contents to quickly jump around.

## Clint's stream

```{r}
#' Remove errors
err <- snipe %>% 
  filter(Clint == "e" |
           swushwoi == "e")

overallW <- snipe %>% 
  anti_join(err)

#' Pivot longer, remove NAs, convert race and result to numerics, factor players
overallL <- overallW %>% 
  pivot_longer(cols = swushwoi:Goio,
               names_to = "player",
               values_to = "result") %>% 
  filter(!is.na(result)) %>% 
  mutate(race = as.numeric(race),
         result = as.numeric(result),
         player = as.factor(player))
```

```{r}
#' Filter by date
mar18 <- overallL %>% 
  filter(date == "2022-03-18")

before <- overallL %>% 
  filter(date < "2022-03-18")
```

```{r include=FALSE}
#' Games per host
mar18 %>% 
  group_by(host) %>% 
  summarise(races = max(race))

#' CC of games per host
overallW %>% 
  filter(date == "2022-03-18") %>% 
  group_by(host) %>% 
  count(cc)

#' Team games per host
overallW %>% 
  filter(date == "2022-03-18") %>% 
  group_by(host) %>% 
  count(team)
```

On March 18th, Clint played 40 games with chat. Creating a private room allowed the options for team games and 200cc Grand Prix. There were 16 games played with teams, 24 without; 16 games were 150cc, 8 were 150cc mirrored, and 16 were 200cc.

```{r include=FALSE}
#' Clint games
hostCS <- mar18 %>% 
  filter(host == "Clint") %>% 
  select(-c(date, room, host))

overallCS <- before %>% 
  select(-c(date, room, host)) %>% 
  bind_rows(hostCS)

#' Clint players
playerCS <- distinct(hostCS, player)

playerCSO <- distinct(before, player)

anti_join(playerCS, playerCSO)
```

### Tracks Played

The table below shows which tracks were played on March 19th.

```{r}
trkFqTYD <- overallCS %>% 
  filter(player == "Clint") %>% 
  count(trk) %>% 
  arrange(desc(n)) %>% 
  mutate(fq = round(n/sum(n)*100, 2),
         trk = as.factor(trk))

trkFq <- hostCS %>%  
  filter(player == "Clint") %>% 
  count(trk) %>% 
  arrange(desc(n)) %>% 
  mutate(fq = round(n/sum(n)*100, 2),
         trk = as.factor(trk)) %>% 
  left_join(trkFqTYD, by = "trk") %>% 
  left_join(tracks) %>% 
  select(track, n.x, fq.x, n.y, fq.y) %>% 
  filter(!is.na(track))

datatable(trkFq, 
          filter = 'top', 
          caption = "Most frequent tracks",
          colnames = c("Track", 
                       "Races Today", 
                       "Frequency",
                       "YTD",
                       "Fq"),
          options = list(pageLength = 8))
```

Unsurprisingly, the new tracks were the most played courses of the night. Included in the top are Coconut Mall and Ninja Hideaway, two fan favorites.

### Players

Aside from Clint, there were 30 people who were able to join and play in his room. For 18 players it was their first time playing with Clint in 2022. The table below shows people who played on March 19th and how many games they've played to date this year.

```{r}
playerFq18 <- hostCS %>% 
  filter(player != "Clint") %>% 
  count(player) %>% 
  arrange(desc(n))

playerFqYTD <- overallCS %>% 
  filter(player != "Clint") %>% 
  count(player) %>% 
  arrange(desc(n))

playerFq18 %>% 
  left_join(playerFqYTD, by = "player") %>% 
  datatable(caption = "March 19th Snipers",
            colnames = c("Player", "Races completed", "YTD"),
          options = list(pageLength = 10))
```

Dozer, Drift King, and fartamor were able to play the most games this day, each playing 32 races. One notable first time player (for 2022) was Xenoda, one of Clint's mods, who played in 16 games.

### Placement Frequency

The two graphs below show result data for Clint and the 7 players who played the most games. The first graph shows the number of *n*th place finishes for each player.

```{r}
vC8 <- c("Clint",
        "Dozer",
        "Drift King",
        "fartamor",
        "HeyIsCarl",
        "plop",
        ".-.",
        "Snurglez"
        )

vC8c <- vC8 %>% str_c(collapse = "|")

C8 <- hostCS %>% 
  filter(str_detect(player, vC8c)) %>% 
  filter(player != "Dark Clint")

C8$player <- factor(C8$player, levels = vC8)

ggC8 <- C8 %>% ggplot(aes(x=result, fill=player)) +
  geom_bar(position = "stack") +
  scale_x_continuous(breaks = seq(1, 12, by = 1)) +
  scale_fill_brewer(palette = "Set3") +
  theme_minimal() +
  labs(title="Placement count for players, March 19, 2022",
       x="Result", 
       y="Count", 
       fill="Player")

ggplotly(ggC8)
```

Snurglez has the most first place finishes, with 11 over the course of the night, followed by plop and Clint.

### Average Results

The graph below shows the smoothed average result for each player. Double click on a name in the legend to isolate the line. Single click to hide/show a racer.

```{r, layout="l-page", fig.height=5}
ggResult <- C8 %>% 
  ggplot(aes(x = race, y = result, color = player, fill = player)) +
  geom_smooth(alpha = 0.15) +
  scale_y_reverse(breaks = seq(1, 12, by = 2)) +
  scale_color_brewer(palette = "Set3") +
  scale_fill_brewer(palette = "Set3") +
  theme_minimal() +
  labs(title = "Smoothed average result for players, March 19, 2022",
       x = "Race #",
       y = "Result",
       color = "Player",
       fill = NULL)

ggplotly(ggResult)
```

Clint, Snurglez, and .-. saw their results fluctuate over the night, while plop placed consistently high. Fartamor had a rough start but showed significant improvement as the games went on, with his starting average around 8th place and his final average around 4th place.

### Rankings

They table below takes the average score for each player and assigns them a ranking. Players are sorted by their March 19th average.

```{r}
CSavg <- hostCS %>% 
  group_by(player) %>% 
  summarise(avg = mean(result),
            plays = n()) %>% 
  arrange(avg)

CSrank <- CSavg %>% 
  mutate(rank = case_when(
    avg < 4 ~ "S",
    avg < 4.5 ~ "A+",
    avg < 5 ~ "A",
    avg < 5.5 ~ "A-",
    avg < 6 ~ "B+",
    avg < 6.5 ~ "B",
    avg < 7 ~ "B-",
    avg < 7.5 ~ "C+",
    avg < 8 ~ "C",
    avg < 8.5 ~ "C-",
    avg < 9 ~ "D+",
    avg < 9.5 ~ "D",
    avg < 10 ~ "D-",
    TRUE ~ "F"
  ),
  avg = round(avg, 2)) %>% 
  arrange(avg) %>% 
  mutate(player = as.factor(player),
         rank = as.factor(rank))
```

```{r}
overallAvg <- overallCS %>% 
  group_by(player) %>% 
  summarise(avg = mean(result),
            plays = n()) %>% 
  arrange(avg)

overallRank <- overallAvg %>% 
  mutate(rank = case_when(
    avg < 4 ~ "S",
    avg < 4.5 ~ "A+",
    avg < 5 ~ "A",
    avg < 5.5 ~ "A-",
    avg < 6 ~ "B+",
    avg < 6.5 ~ "B",
    avg < 7 ~ "B-",
    avg < 7.5 ~ "C+",
    avg < 8 ~ "C",
    avg < 8.5 ~ "C-",
    avg < 9 ~ "D+",
    avg < 9.5 ~ "D",
    avg < 10 ~ "D-",
    TRUE ~ "F"
  ),
  avg = round(avg, 2)) %>% 
  arrange(avg) %>% 
  mutate(player = as.factor(player),
         rank = as.factor(rank))

CSrank %>% 
  left_join(overallRank, by = "player") %>% 
  select(player, avg.x, rank.x, avg.y, rank.y) %>% 
  datatable(colnames = c("Player", "Today's Average", "Today's Rank", "Overall Average", "Overall Rank"),
            caption = "Player Rankings",
          options = list(pageLength = 10))
```

Jihyo, already established as an S-tier player, dominated in the games they played, averaging a 2nd place finish. Snurglez and plop also had great nights, averaging in the S-tier.

The most improved player was Dylan, who ranked as D+ [in the previous rankings I tallied](https://sarah.fyi/mk/2022-03-15-snipe/#rankings). On March 19th, Dylan averaged an A rank, bringing his overall rank up to a C. Clint's overall rank continues to be a B+, though his average slightly improved from 5.8 to 5.67.

## swushwoi's stream

As I mentioned in the intro, I was not able to play in Clint's games but I joined the lobby of another streamer, swushwoi, who was playing with other people who regularly play with Clint.

There were 12 players in swushwoi's stream, three of whom played with Clint earlier in the night: swushwoi, zipcola, and FruitYoshi. Additionally, myself and mooney have played with Clint before but not that night.

In swushwoi's stream, 41 races were played, 24 on teams and 17 without. Of the races, 25 were 150cc and 16 were 200cc.

```{r}
#' swushwoi games
hostSW <- mar18 %>% 
  filter(host == "swushwoi") %>% 
  select(-c(date, room, host))

#' swushwoi players
playerSW <- distinct(hostSW,  player)
```

```{r eval=FALSE, include=FALSE}
semi_join(playerCS, playerSW)
```

The table below shows the average result for players in swushwoi's stream.

```{r}
SWavg <- hostSW %>% 
  group_by(player) %>% 
  summarise(avg = mean(result),
            plays = n()) %>% 
  arrange(avg)

SWrank <- SWavg %>% 
  mutate(rank = case_when(
    avg < 4 ~ "S",
    avg < 4.5 ~ "A+",
    avg < 5 ~ "A",
    avg < 5.5 ~ "A-",
    avg < 6 ~ "B+",
    avg < 6.5 ~ "B",
    avg < 7 ~ "B-",
    avg < 7.5 ~ "C+",
    avg < 8 ~ "C",
    avg < 8.5 ~ "C-",
    avg < 9 ~ "D+",
    avg < 9.5 ~ "D",
    avg < 10 ~ "D-",
    TRUE ~ "F"
  ),
  avg = round(avg, 2)) %>% 
  arrange(avg) %>% 
  mutate(player = as.factor(player),
         rank = as.factor(rank))

SWrank %>% 
  select(player, avg, rank) %>% 
  datatable(colnames = c("Player", "Average", "Rank"),
            caption = "Player Rankings",
          options = list(pageLength = 12))
```

Mooney, a legend in Clint's stream, averaged an insane 1.22 placement over the night. Everyone who played in Clint's stream averaged significantly better in this lobby: FruitYoshi went from a 5.75 to a 3.61; zipcola from a 7.12 to a 5.62; and swushwoi from a 9.45 to a 6.93. I averaged 6th place, a solid B ranking.

## Overall

### Clint's Best/Worst Tracks

The table below shows Clint's average result for each track and how many times he has played it this year. Note that tracks that have only been played a few times likely have less reliable data.

```{r}
CStrk <- overallL %>% 
  filter(player == "Clint") %>% 
  left_join(tracks, by = "trk") %>% 
  mutate(track = as.factor(track)) %>% 
  group_by(track) %>% 
  summarise(avg = mean(result),
            plays = n()) %>% 
  mutate(avg = round(avg, 2)) %>% 
  arrange(avg)

datatable(CStrk, 
          filter = 'top', 
          colnames = c("Track", "Average", "Plays"),
          caption = "Clint's average result for MK8DX tracks in 2022")
```

I hope others find this table useful for prediction betting in future streams.

### Player Rankings

Lastly, let's look at the overall rankings for people who have played at least five games in the Clint Stevens Mario Kart extended universe. This includes people who did not play in Clint's March 19th stream and those who played in swushwoi's stream.

```{r}
oAvg <- overallL %>% 
  group_by(player) %>% 
  summarise(avg = mean(result),
            plays = n()) %>% 
  filter(plays > 4) %>% 
  arrange(avg)

oRank <- oAvg %>% 
  mutate(rank = case_when(
    avg < 4 ~ "S",
    avg < 4.5 ~ "A+",
    avg < 5 ~ "A",
    avg < 5.5 ~ "A-",
    avg < 6 ~ "B+",
    avg < 6.5 ~ "B",
    avg < 7 ~ "B-",
    avg < 7.5 ~ "C+",
    avg < 8 ~ "C",
    avg < 8.5 ~ "C-",
    avg < 9 ~ "D+",
    avg < 9.5 ~ "D",
    avg < 10 ~ "D-",
    TRUE ~ "F"
  ),
  avg = round(avg, 2)) %>% 
  arrange(avg) %>% 
  mutate(player = as.factor(player),
         rank = as.factor(rank))

oRank %>% 
  select(player, avg, rank, plays) %>% 
  datatable(colnames = c("Player", "Average", "Rank", "Games"),
            caption = "Player Rankings",
          options = list(pageLength = 10))
```

Ideally this table would show a weighted average, where the number of games played and the difficulty of the room factor into a person's rank. I'm not quite sure how to do this but if you have any ideas feel free to whisper me on Twitch.

## Final Words

Collecting this Mario Kart data has been a fun project for the past month. I hope others find it as interesting as I do. I initially collected data for just Clint and myself, but it didn't feel right to leave out the rest of the community, even though it took some extra time to gather everyone's data. I love that I've been able to document a community of people coming together to play some games.

I'll be starting a full time job the day after creating this post. I'm not sure how often I'll be able to keep playing in games or keep up with the data. However, all of the data I've collected I've made [public on GitHub](https://github.com/sj-io/sarahFYI/blob/main/_mk/_data/stream-snipe.csv), so in the event I'm not able to continue this and someone else wishes to, please feel free to use what I've already collected.[^2] You can also check the RMarkdown files to see how I used it (sorry it's a bit of a mess).

[^2]: Note: This post was the first one I began collecting data on whether courses were mirrored.

Love you all,

Sarah
